

% ==============================================================================
% START: Introduction
% ==============================================================================
\section{Introduction}

The application is the last requirement to graduate from Udacity's Data Engineering Nano degree. The following is
the overview of the project as stated on Udacity page course. \\

\emph{The purpose of the data engineering capstone project is to give you a chance to 
combine what you've learned throughout the program. This project will be an important part of 
your portfolio that will help you achieve your data engineering-related career goals.}


\subsection{My vision}
The project has two main parts. The back end was designed to run in the cloud. This includes storage in S3 (raw files and the parquet model), EMR processing, and relational database in Redshift. This would allow this back-end to serve multiple applications. The other part would be
the front end, on the local / client side, this means that a local user is expected to have the web interface Flask. This would allow him/her to query the Redshift database plus the additional ability to ask questions about documents of interest. I imagine a local user, setting up the flask app and then browsing the database with it, then later indexing on their local elastic search server, the abstract and title of the article of interest, this could mean
filtering by a particular topic, year, or author. After the indexing, the user can ask questions of the type \emph{what do we know about the uncertainty principle?}. The answer will come on the form of a bootstrap card, with scores, possible answers, full paper URL pdf access to the document. The question and answering system is possible with \href{https://github.com/deepset-ai/haystack}{haystack}. The following are the core features of haystack on their github.




\begin{itemize}
\item Powerful ML models: Utilize all latest transformer based models (BERT, ALBERT, RoBERTa ...)
\item Modular \& future-proof: Easily switch to newer models once they get published.
\item Developer friendly: Easy to debug, extend and modify.
\item Scalable: Production-ready deployments via Elasticsearch backend \& REST API
\item Customizable: Fine-tune models to your own domain \& improve them continuously via user feedback
\end{itemize}


    
    
    
    


% ==============================================================================
% START: Introduction
% ==============================================================================